\section{Overall Description}
\subsection{Product Perspective}
	Flatfindr is a self-contained product that has no connections to other software.	

\subsection{Product Functions}
\begin{itemize}
	\item Creating / viewing ads for flats and studios
	\item Linking roommates to ads
	\item General search functionality with specific criteria
	\item Scheduling visits
	\end{itemize}

\subsection{User Classes and Characteristics}
	\subsubsection{User}
		The general user that presumably is looking for a new place to live will be the largest 
		user class. Their satisfaction depends on the ads and hereby indirectly from the Advertiser 
		user class, as well as on crucial functionalities in the system, such as a customisable 
		search and a smooth way of interacting with advertisers.

	\subsubsection{Advertiser}
		The user class that creates ads is called advertiser. Advertisers are the most important 
		user class to satisfy. This depends strongly on the ad-creating interface, which should be 
		as easy as possible to use. 

	\subsubsection{Roommate}
		A roommate is someone who was linked to an ad by an advertiser. Their goals differ from 
		the general user in the way that they generally are not looking for a new place, but are 
		instead supporting the advertisers. Their satisfaction depends on their possibility to 
		schedule events easily.
	
	\subsubsection{Premium User}
		By paying a fee for additional features, the premium user strongly increases the resources 
		of the programming team. If the premium features are beneficial to the general user, the 
		quantity of premium users will be optimal.
		
\subsection{Operating Environment}
	Flatfindr runs on any frequently used browser, i.e. Firefox, Safari, Chrome, Microsoft Edge, Internet Explorer.
	
\subsection{Design and Implementation Constraints}
	The template of Flatfindr was delivered using Java, MySQL, Hibernation and JavaScript. Changing this would 
	present unnecessary additional effort, which is why, in this way, we are constrained by these frameworks and languages.\\
	The software should be maintainable, so object-oriented design will be best-practice.
	Other than that, there seem to be no requirements, especially security.